A GRASP algorithm for the concrete delivery problem.

### 2023-08-21 Article/article.tex
Article with comparison between LS et noLS

A customer $i$ requests one or more types of concrete to be delivered to their construction site on a specific day, with the delivery service starting at the due time $a_i$.  We call an order $o$ a request for a specific type of concrete. $q_i$ is the sum of the demands $q_o$ of each order $o$ placed, $a_i$ is the desired arrival time of the first concrete mixer, and $\tau^u_i$ is the unloading rate for customer $i$. If the order requires more concrete than a single truck can carry, multiple deliveries are scheduled.

@@

@@

Constraints (\ref{mod:c8}) - - (\ref{mod:c10}) ensure that the first service of any customer $i$ must start at the due time $a_i$. This first service may be performed at the first delivery node of any order $\in O_i$, and one order must be completed before another is started. It also enforces the precedence constraints between the last delivery of an order and the first delivery of the following order.
Constraints (\ref{mod:c11}) - - (\ref{mod:c15}) find the delivery sequence of all orders $\in \mathcal{O}_i$. With constraints (\ref{mod:c16}) - - (\ref{mod:c19}), two trucks cannot unload at the same time for consecutive deliveries of the same order. Additionally, these constraints impose a maximum time delay between the two trucks. Similarly, constraints (\ref{mod:c20}) - - (\ref{mod:c23}) ensure that two trucks cannot be loaded at the same time at a plant. Constraints (\ref{mod:c24}) require that the cumulative load of all concrete mixers serving an order must equal the required quantities, and (\ref{mod:c240}) bound a driver load.  Constraints (\ref{mod:c25}) require that a driver can only visit a loading/delivery node once. Constraints (\ref{mod:c26}) are degree constraints. Constraints (\ref{mod:c29}) - - (\ref{mod:c30}) calculate the difference between a driver's hours of service and the minimum and normal hours of service. Finally, constraints (\ref{mod:c31}) - - (\ref{mod:cend}) define the nature and bounds of the variables.

@@

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    %    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}                                                 & \multicolumn{1}{c}{Value} \\ \midrule
        Unloading duration ($\tau_c^u$)                                               & 2 min$/m^3$               \\
        Cleaning duration ($\rho$)                                                    & 10 min                    \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
    %    }
\end{table}
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).
The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average and the best values of the objective function when solving each instance five times. All daily orders are served by our algorithm within these five replications. On average, five instances require multiple runs of the algorithm to successfully serve all customers, as shown in column $UQ$, which is the undelivered quantity. The sum of the driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put certain drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase the travel costs ($TC$).

$FDD$ is the sum of the delays of the first deliveries.  For the small instances, all but one of the first deliveries are on time. For the other instances, there is at least one customer with a late first delivery.
To get an idea of the actual delay per customer, we report $mFDD$, which is the maximum delay of all first deliveries. This tells us that we have a maximum delay that varies between 0 and 19 minutes for small instances, 3.5 and 60 minutes for medium instances, and 24 to 60 minutes for large instances.
    \caption{Results with all instances}
    \label{tab:all_instances}
    \begin{tabular}{llccccccccccccc}
    &                 &          & \multicolumn{6}{c}{Avg} & \multicolumn{6}{c}{Best}   \\
    \cmidrule(l){4-9} \cmidrule(l){10-15}
    &  & Demand   & $UQ$   & $TC$  & $FDD$    & $DUC$    & $DOC$    & \multirow[c]{2}{*}{Z} & $TC$      & $FDD$    & $mFDD$  & $DUC$    & $DOC$    & \multirow[c]{2}{*}{Z} \\
        & & ($m^3$)  & ($m^3$) & (min)  & (min)    & (min)    & (min)    &     & (min)     & (min)    & (min) & (min)   &(min)& \\
        \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 0.0 & 1,243.5 & 0.0 & 37.7 & 0.0 & 2,373.9 & 1,243.5 & 0.0 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
        & C_13_5_8_1 & 267.0 & 0.0 & 745.1 & 0.0 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 \\
        & C_18_6_11_2 & 333.5 & 0.0 & 753.3 & 0.0 & 194.7 & 0.0 & 6,593.7 & 753.3 & 0.0 & 0.0 & 125.3 & 0.0 & 4,513.2 \\
        & C_15_4_7_2 & 375.0 & 0.0 & 1,014.9 & 0.0 & 132.8 & 291.6 & 10,830.8 & 1,014.2 & 0.0 & 0.0 & 172.1 & 76.1 & 7,700.1 \\
        & C_19_7_8_2 & 388.0 & 0.0 & 1,765.5 & 0.0 & 314.8 & 150.9 & 14,225.6 & 1,745.8 & 0.0 & 0.0 & 224.5 & 87.9 & 10,237.1 \\
        & C_29_10_14_3 & 613.5 & 0.0 & 3,742.0 & 48.6 & 211.0 & 735.6 & 73,392.7 & 3,628.8 & 49.2 & 18.8 & 112.9 & 547.2 & 67,145.2 \\
        & C_31_8_11_3 & 776.0 & 0.0 & 2,330.6 & 0.0 & 781.6 & 656.5 & 38,909.6 & 2,297.2 & 0.0 & 0.0 & 606.7 & 567.0 & 31,836.1 \\
        & C_35_9_10_3 & 937.5 & 0.0 & 4,175.3 & 0.0 & 341.8 & 1,329.5 & 41,021.0 & 4,174.4 & 0.0 & 0.0 & 221.7 & 1,161.6 & 34,057.0 \\
        \cmidrule(l){1-15}
        \multirow[c]{14}{*}{Medium} & C_76_40_43_6 & 1,160.5 & 0.0 & 6,311.6 & 17.2 & 3,014.6 & 706.0 & 128,106.4 & 5,967.0 & 6.2 & 3.5 & 2,961.6 & 644.4 & 113,884.7 \\
        & C_104_42_47_8 & 1,565.0 & 0.0 & 9,358.2 & 34.1 & 3,890.1 & 679.0 & 173,754.5 & 9,777.5 & 32.0 & 13.0 & 2,830.0 & 240.6 & 131,507.6 \\
        & C_94_63_70_7 & 1,746.5 & 0.0 & 14,369.1 & 90.2 & 1,353.9 & 1,391.4 & 173,007.0 & 14,428.7 & 78.9 & 19.3 & 1,147.9 & 1,464.3 & 157,038.1 \\
        & C_116_67_78_8 & 1,839.5 & 0.0 & 13,602.9 & 67.9 & 2,419.4 & 857.3 & 171,229.1 & 13,871.9 & 67.2 & 33.2 & 2,347.7 & 523.3 & 162,021.5 \\
        & C_116_71_82_8 & 2,060.0 & 0.0 & 12,678.2 & 158.6 & 1,991.3 & 1,125.8 & 253,575.1 & 12,089.7 & 147.7 & 27.2 & 1,966.0 & 922.7 & 237,183.6 \\
        & C_117_57_70_6 & 2,327.5 & 0.0 & 15,495.0 & 142.4 & 1,388.6 & 1,680.5 & 233,181.4 & 15,153.3 & 114.2 & 22.2 & 1,823.7 & 1,671.5 & 217,448.3 \\
        & C_137_79_83_7 & 2,425.0 & 0.0 & 18,960.4 & 375.8 & 2,124.7 & 1,857.9 & 495,614.5 & 18,360.3 & 335.1 & 34.2 & 2,552.7 & 1,794.2 & 465,977.3 \\
        & C_127_66_80_8 & 2,512.5 & 0.0 & 16,033.3 & 10.4 & 1,579.6 & 1,552.1 & 104,879.1 & 17,599.1 & 14.4 & 5.0 & 1,046.3 & 1,242.3 & 88,203.5 \\
        & C_128_68_74_7 & 2,595.0 & 0.0 & 19,774.4 & 361.6 & 944.6 & 2,616.7 & 461,998.2 & 18,728.8 & 191.0 & 42.5 & 1,418.8 & 2,841.2 & 309,116.8 \\
        & C_136_85_97_8 & 2,673.0 & 0.0 & 18,223.6 & 188.5 & 2,134.5 & 2,352.2 & 317,811.4 & 18,894.6 & 137.4 & 48.6 & 1,155.6 & 2,137.0 & 233,669.0 \\
        & C_128_78_85_8 & 2,685.5 & 0.0 & 18,463.9 & 305.8 & 1,277.3 & 3,157.0 & 425,759.3 & 18,041.6 & 192.4 & 35.7 & 1,374.3 & 3,234.2 & 316,314.1 \\
        & C_131_77_85_8 & 2,893.5 & 0.0 & 18,003.0 & 212.6 & 1,248.7 & 1,716.1 & 302,370.4 & 18,063.0 & 200.2 & 43.2 & 780.7 & 1,539.1 & 272,509.6 \\
        & C_137_89_97_7 & 2,939.5 & 0.0 & 23,293.0 & 636.0 & 849.9 & 3,523.9 & 755,280.5 & 22,038.1 & 438.3 & 58.6 & 849.8 & 3,461.1 & 555,029.1 \\
        & C_133_84_98_7 & 2,971.0 & 18.7 & 22,000.0 & 1,157.6 & 805.4 & 2,291.4 & 1,249,585.1 & 20,992.6 & 1,061.2 & 59.4 & 546.1 & 2,742.5 & 1,153,396.1 \\
        \cmidrule(l){1-15}
        \multirow[c]{14}{*}{Large} & C_132_98_109_8 & 3,078.5 & 0.0 & 23,469.1 & 247.4 & 548.7 & 4,162.3 & 370,622.5 & 23,425.8 & 160.9 & 29.4 & 493.2 & 4,426.1 & 287,683.7 \\
        & C_129_101_119_8 & 3,229.0 & 0.0 & 19,051.7 & 269.0 & 1,232.1 & 3,820.4 & 401,387.9 & 19,453.3 & 166.7 & 35.8 & 1,138.1 & 4,719.6 & 314,728.3 \\
        & C_141_114_136_8 & 3,350.5 & 8.7 & 21,505.6 & 1,127.2 & 1,422.7 & 2,339.2 & 1,238,202.0 & 21,863.2 & 943.9 & 55.4 & 1,177.0 & 2,513.4 & 1,051,386.9 \\
        & C_140_114_132_8 & 3,401.5 & 0.0 & 23,938.4 & 1,055.1 & 910.2 & 3,269.1 & 1,171,715.1 & 23,969.7 & 988.5 & 54.4 & 981.3 & 3,253.1 & 1,107,019.4 \\
        & C_143_101_123_8 & 3,437.5 & 0.0 & 25,711.0 & 352.2 & 903.0 & 4,085.1 & 486,755.0 & 26,284.9 & 335.5 & 43.5 & 566.1 & 3,913.0 & 457,007.0 \\
        & C_137_112_129_8 & 3,471.0 & 0.0 & 22,562.4 & 340.8 & 402.4 & 3,371.1 & 442,869.1 & 22,338.3 & 275.1 & 45.6 & 375.2 & 3,819.8 & 385,076.1 \\
        & C_142_114_129_8 & 3,499.5 & 0.0 & 22,478.3 & 801.0 & 1,294.8 & 4,168.2 & 945,633.4 & 22,387.6 & 654.6 & 55.3 & 1,090.4 & 4,472.6 & 799,184.0 \\
        & C_149_98_122_8 & 3,513.0 & 3.0 & 20,767.5 & 778.4 & 2,236.9 & 2,852.2 & 923,357.9 & 21,224.7 & 684.5 & 51.1 & 2,267.6 & 3,046.6 & 834,708.6 \\
        & C_139_98_108_8 & 3,541.0 & 0.0 & 21,613.4 & 661.0 & 852.3 & 3,716.2 & 782,546.8 & 22,043.2 & 522.3 & 51.6 & 482.8 & 3,648.5 & 631,819.8 \\
        & C_144_108_122_8 & 3,670.5 & 0.0 & 24,738.3 & 746.0 & 664.9 & 3,465.8 & 860,025.7 & 25,806.9 & 675.4 & 50.4 & 548.5 & 3,209.2 & 781,866.1 \\
        & C_142_92_107_8 & 3,684.5 & 0.0 & 24,553.3 & 298.6 & 644.2 & 4,423.6 & 431,001.0 & 23,586.4 & 182.6 & 24.0 & 803.0 & 4,396.5 & 318,243.2 \\
        & C_138_114_136_8 & 3,739.5 & 0.0 & 25,366.9 & 791.5 & 668.6 & 5,501.8 & 946,993.9 & 23,639.0 & 600.4 & 55.2 & 1,230.8 & 5,314.0 & 767,223.0 \\
        & C_150_127_136_8 & 3,946.5 & 0.0 & 25,785.2 & 613.8 & 629.1 & 4,686.4 & 752,189.6 & 27,332.9 & 507.3 & 57.1 & 250.3 & 5,295.7 & 648,057.4 \\
        & C_148_112_131_8 & 3,953.5 & 6.9 & 26,231.2 & 1,002.0 & 517.8 & 3,467.4 & 1,113,149.3 & 25,559.2 & 886.9 & 56.0 & 559.3 & 4,213.2 & 1,013,500.2 \\

@@

\begin{table}[htbp]
    \centering
    \caption{RMC delivered within different runtimes}
    \label{tab:runtime}
    \scriptsize
    \resizebox*{0.7\textwidth}{!}{
        \begin{tabular}{lcccccc}
            \toprule
                                    &        & \multicolumn{5}{c}{Runtime (min)}                                   \\
            \cmidrule{3-7}
                                    &        & 1                                 & 5      & 10     & 30    & 60    \\
            \midrule
            \multirow{1}{*}{Small}  & \%Load & 100.00                            & 100.00 & 100.00 & 100.0 & 100.0 \\
            %   & \#Instance &  8 &    8 &    8 &    8 & 8 \\
            \cmidrule{2-7}
            \multirow{1}{*}{Medium} & \%Load & 99.71                             & 99.93  & 99.86  & 100.0 & 100.0 \\
            %   & \#Instance &   11 &   13 &   13 &   14 &   14 \\
            \cmidrule{2-7}
            \multirow{1}{*}{Large}  & \%Load & 99.64                             & 99.64  & 99.79  & 100.0 & 100.0 \\
            %   & \#Instance &   10 &   10 &   12 &   14 &   14 \\
            \bottomrule
        \end{tabular}
    }

@@

>>>>

A customer $i$ requests one or more types of concrete to be delivered to their construction site on a specific day, with the delivery service starting at the due time $a_i$.  We call an order $o$ a request for a specific type of concrete. $q_i$ is the sum of the demands $q_o$ of each order $o$ placed, $a_i$ is the desired arrival time of the first concrete mixer, and $\tau^u_i$ is the unloading rate for customer $i$. If the order requires more concrete than a single truck can carry, multiple deliveries are scheduled. We will accept a first delivery if it arrives within a time window of $\left[a_i, a_i + \tau^w \right]$, where $\tau^w_i$ is an user-defined parameter.

@@

    \label{mod:c91}  & g_{i} - a_i \leq \tau^w  & \hspace{-20mm}  \forall  i \in \mathcal{C}  \\

@@

Constraints (\ref{mod:c8}) - - (\ref{mod:c10}) ensure that the first service of any customer $i$ must start after the due time $a_i$. This first service may be performed at the first delivery node of any order $\in O_i$, and one order must be completed before another is started. It also enforces the precedence constraints between the last delivery of an order and the first delivery of the following order.
Constraints (\ref{mod:c11}) - - (\ref{mod:c15}) find the delivery sequence of all orders $\in \mathcal{O}_i$. With constraints (\ref{mod:c16}) - - (\ref{mod:c19}), two trucks cannot unload at the same time for consecutive deliveries of the same order. Additionally, these constraints impose a maximum time delay between the two trucks. Similarly, constraints (\ref{mod:c20}) - - (\ref{mod:c23}) ensure that two trucks cannot be loaded at the same time at a plant. Constraints (\ref{mod:c24}) require that the cumulative load of all concrete mixers serving an order must equal the required quantities, and (\ref{mod:c240}) bound a driver load.  Constraints (\ref{mod:c25}) require that a driver can only visit a loading/delivery node once. Constraints (\ref{mod:c26}) are degree constraints. Constraints (\ref{mod:c29}) - - (\ref{mod:c30}) calculate the difference between a driver's hours of service and the minimum and normal hours of service. Finally, constraints (\ref{mod:c31}) - - (\ref{mod:cend}) define the nature and bounds of the variables.

@@

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    %    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}  &
        \multicolumn{1}{c}{Value} \\ \midrule
 Time window ($\tau^w$)  & 60 min    \\
 Unloading duration ($\tau_c^u$)  & 2 min$/m^3$   \\
 Cleaning duration ($\rho$)    & 10 min  \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
    %    }
\end{table}
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).
The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average and the best values of the objective function when solving each instance five times. All daily orders of the small instances are completely served by our algorithm within these five replications, as shown in column $UQ$, which reports the undelivered quantity. $99.57\%$ and $99.5\%$ of the total demands are served for the medium and large sets. The sum of the driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put certain drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase the travel costs ($TC$).

$FDD$ is the sum of the delays of the first deliveries.  For the small instances, all but one of the first deliveries are on time. For the other instances sets, there is at least one customer with a late first delivery.
To get an idea of the actual delay per customer, we report $mFDD$, which is the maximum delay of all first deliveries. This tells us that we have a maximum delay that varies between 0 and $35.7$ minutes for small instances, $16.8$ and $60$ minutes for medium instances, and $56$ to 60 minutes for large instances.

\begin{table}[!ht]
    \centering
    \caption{Results with all instances}
    \label{tab:all_instances}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{llcccccccccccccc}
    \toprule
    &                 &          & \multicolumn{6}{c}{Avg} & \multicolumn{6}{c}{Best}  \\
    \cmidrule(l){4-9} \cmidrule(l){10-16}
     &  & Demand & $TC$ & $UQ$ & $FDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} & $TC$ & $UQ$ & $FDD$ & $mFDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} \\
     &  & ($m^3$) & (min) & ($m^3$) & (min) & (min) & (min) &  & (min) & ($m^3$) & (min) & (min) & (min) & (min) &  \\
    \midrule
    \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 1,243.5 & 0.0 & 0.0 & 10.8 & 0.0 & 1,568.3 & 1,243.5 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
     & C_13_5_8_1 & 267.0 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 \\
     & C_18_6_11_2 & 333.5 & 753.3 & 0.0 & 0.0 & 145.9 & 0.0 & 5,130.0 & 753.3 & 0.0 & 0.0 & 0.0 & 118.7 & 0.0 & 4,315.1 \\
     & C_15_4_7_2 & 375.0 & 1,015.6 & 0.0 & 0.0 & 148.2 & 150.5 & 8,470.9 & 1,015.4 & 0.0 & 0.0 & 0.0 & 123.4 & 110.3 & 6,924.5 \\
     & C_19_7_8_2 & 388.0 & 1,747.2 & 0.0 & 0.0 & 349.8 & 159.0 & 15,421.6 & 1,781.8 & 0.0 & 0.0 & 0.0 & 186.0 & 0.0 & 7,361.5 \\
     & C_29_10_14_3 & 613.5 & 3,510.1 & 0.0 & 59.5 & 194.6 & 331.9 & 75,488.1 & 3,493.4 & 0.0 & 59.5 & 35.7 & 120.5 & 60.0 & 67,810.4 \\
     & C_31_8_11_3 & 776.0 & 2,314.8 & 0.0 & 0.0 & 804.3 & 640.7 & 39,256.8 & 2,278.2 & 0.0 & 0.0 & 0.0 & 503.5 & 617.0 & 29,722.9 \\
     & C_35_9_10_3 & 937.5 & 4,175.5 & 0.0 & 0.0 & 222.1 & 669.3 & 24,224.7 & 4,163.1 & 0.0 & 0.0 & 0.0 & 243.3 & 570.0 & 22,863.2 \\
     \cmidrule(l){1-16}

    \multirow[c]{14}{*}{Medium} & C_76_40_43_6 & 1,160.5 & 6,055.8 & 0.0 & 49.1 & 3,286.4 & 990.0 & 173,509.5 & 5,990.6 & 0.0 & 33.9 & 25.4 & 3,061.3 & 788.6 & 147,510.1 \\
     & C_104_42_47_8 & 1,565.0 & 8,107.1 & 12.0 & 53.3 & 3,637.1 & 119.4 & 1,372,936.3 & 8,301.9 & 12.0 & 54.3 & 16.8 & 3,200.5 & 140.1 & 1,361,393.1 \\
     & C_94_63_70_7 & 1,746.5 & 13,783.0 & 0.0 & 238.7 & 983.2 & 1,554.6 & 313,077.0 & 13,673.5 & 0.0 & 195.9 & 59.7 & 1,025.2 & 1,407.3 & 268,524.2 \\
     & C_116_67_78_8 & 1,839.5 & 13,456.8 & 0.0 & 132.7 & 1,869.0 & 614.3 & 214,501.3 & 13,484.8 & 0.0 & 98.0 & 22.7 & 1,792.8 & 622.4 & 177,710.8 \\
     & C_116_71_82_8 & 2,060.0 & 11,393.8 & 9.0 & 265.1 & 2,714.8 & 1,054.6 & 1,279,068.9 & 10,793.3 & 9.0 & 242.0 & 41.8 & 3,197.9 & 665.2 & 1,262,000.5 \\
     & C_117_57_70_6 & 2,327.5 & 14,975.0 & 0.0 & 324.1 & 1,005.5 & 1,149.6 & 392,281.0 & 15,303.5 & 0.0 & 295.2 & 54.6 & 659.4 & 1,083.8 & 351,940.4 \\
     & C_137_79_83_7 & 2,425.0 & 17,644.3 & 0.0 & 553.8 & 2,320.4 & 1,993.3 & 680,888.1 & 17,379.3 & 0.0 & 474.0 & 55.7 & 2,964.4 & 2,016.3 & 620,601.6 \\
     & C_127_66_80_8 & 2,512.5 & 14,584.3 & 0.0 & 128.3 & 1,600.0 & 1,451.5 & 219,949.8 & 14,499.2 & 0.0 & 127.5 & 47.3 & 1,390.2 & 1,212.8 & 207,962.2 \\
     & C_128_68_74_7 & 2,595.0 & 18,450.6 & 3.7 & 566.6 & 1,317.5 & 2,706.2 & 1,048,712.1 & 18,261.4 & 0.0 & 473.4 & 56.0 & 1,764.7 & 2,525.6 & 595,143.5 \\
     & C_136_85_97_8 & 2,673.0 & 16,831.6 & 0.0 & 379.9 & 2,702.4 & 2,368.0 & 525,199.5 & 17,241.3 & 0.0 & 323.7 & 50.2 & 2,190.5 & 2,767.1 & 461,973.3 \\
     & C_128_78_85_8 & 2,685.5 & 15,679.8 & 63.0 & 474.5 & 1,399.6 & 2,394.4 & 6,880,077.6 & 15,830.6 & 63.0 & 432.7 & 57.8 & 1,206.8 & 2,272.7 & 6,830,154.3 \\
     & C_131_77_85_8 & 2,893.5 & 16,988.0 & 0.0 & 374.5 & 1,557.9 & 1,996.1 & 478,106.8 & 16,565.6 & 0.0 & 352.1 & 44.6 & 1,624.3 & 1,322.5 & 443,865.0 \\
     & C_137_89_97_7 & 2,939.5 & 21,716.4 & 9.8 & 924.4 & 821.0 & 3,494.4 & 2,020,622.6 & 21,311.3 & 0.0 & 799.5 & 51.8 & 887.3 & 3,486.7 & 917,162.4 \\
     & C_133_84_98_7 & 2,971.0 & 20,435.5 & 46.1 & 1,141.3 & 894.1 & 2,127.8 & 5,841,090.1 & 20,520.4 & 9.0 & 1,411.0 & 59.5 & 705.0 & 1,871.9 & 2,390,157.6 \\
     \cmidrule(l){1-16}
    \multirow[c]{14}{*}{Large} & C_132_98_109_8 & 3,078.5 & 22,994.6 & 0.0 & 465.5 & 496.5 & 3,804.8 & 579,471.0 & 22,712.7 & 0.0 & 351.5 & 56.2 & 803.2 & 4,011.3 & 478,549.4 \\
     & C_129_101_119_8 & 3,229.0 & 17,323.1 & 11.0 & 657.8 & 1,577.6 & 2,375.9 & 1,869,937.5 & 17,311.8 & 11.0 & 598.8 & 58.4 & 1,507.7 & 1,948.1 & 1,800,315.9 \\
     & C_141_114_136_8 & 3,350.5 & 19,891.6 & 39.1 & 1,255.8 & 1,366.2 & 2,251.9 & 5,271,698.5 & 19,556.2 & 18.0 & 1,366.7 & 57.9 & 1,380.0 & 2,695.1 & 3,281,568.6 \\
     & C_140_114_132_8 & 3,401.5 & 21,917.6 & 23.8 & 1,254.1 & 680.1 & 3,389.9 & 3,744,172.5 & 22,590.2 & 17.5 & 1,248.5 & 58.7 & 766.3 & 3,267.6 & 3,109,441.2 \\
     & C_143_101_123_8 & 3,437.5 & 23,477.2 & 0.0 & 677.7 & 955.5 & 4,369.4 & 817,244.5 & 23,806.9 & 0.0 & 617.3 & 56.0 & 1,302.2 & 5,147.9 & 783,123.1 \\
     & C_137_112_129_8 & 3,471.0 & 22,089.2 & 0.0 & 546.6 & 544.8 & 4,187.3 & 668,737.0 & 21,195.2 & 0.0 & 456.6 & 55.0 & 883.9 & 3,532.1 & 574,935.0 \\
     & C_142_114_129_8 & 3,499.5 & 20,678.2 & 35.7 & 1,007.5 & 1,119.7 & 4,133.1 & 4,714,436.9 & 21,243.7 & 21.0 & 907.0 & 59.8 & 1,038.0 & 4,016.6 & 3,139,750.0 \\
     & C_149_98_122_8 & 3,513.0 & 19,859.0 & 28.4 & 1,141.7 & 2,154.6 & 2,649.9 & 4,119,224.3 & 19,602.8 & 21.0 & 859.2 & 55.7 & 2,342.9 & 2,728.2 & 3,103,676.6 \\
     & C_139_98_108_8 & 3,541.0 & 21,060.5 & 0.0 & 966.2 & 684.9 & 3,585.4 & 1,079,477.1 & 21,084.8 & 0.0 & 867.2 & 59.8 & 834.9 & 4,133.9 & 996,046.7 \\
     & C_144_108_122_8 & 3,670.5 & 23,330.4 & 2.0 & 1,123.4 & 536.2 & 3,251.6 & 1,427,866.8 & 22,882.8 & 0.0 & 969.7 & 57.8 & 649.7 & 3,587.1 & 1,083,850.9 \\
     & C_142_92_107_8 & 3,684.5 & 23,179.0 & 0.0 & 578.3 & 384.1 & 4,260.4 & 698,184.4 & 23,610.6 & 0.0 & 449.2 & 59.8 & 315.7 & 4,257.2 & 567,403.7 \\
     & C_138_114_136_8 & 3,739.5 & 23,614.6 & 11.7 & 1,225.1 & 837.4 & 5,668.6 & 2,557,166.5 & 22,859.0 & 7.5 & 1,107.0 & 58.3 & 1,224.2 & 5,078.2 & 2,018,119.1 \\
     & C_150_127_136_8 & 3,946.5 & 24,940.3 & 0.0 & 949.5 & 775.5 & 5,384.3 & 1,105,391.3 & 24,939.2 & 0.0 & 829.0 & 57.1 & 805.9 & 6,166.7 & 1,001,490.6 \\
     & C_148_112_131_8 & 3,953.5 & 24,286.0 & 34.0 & 1,247.8 & 657.0 & 3,009.5 & 4,752,026.9 & 24,221.7 & 24.5 & 1,118.5 & 57.1 & 859.7 & 3,483.3 & 3,688,169.1 \\

@@

\begin{table}[!ht]
    \centering
    \caption{RMC delivered within different runtimes}
    \label{tab:runtime}
    \scriptsize
    \resizebox*{0.7\textwidth}{!}{
    \begin{tabular}{llrrrrr}
    \toprule
     &  & \multicolumn{5}{c}{Runtime (min)} \\
     \cmidrule{3-7}
     &  & 1 & 5 & 10 & 30 & 60 \\
    \midrule
    Small & \%Load & 100.00 & 100.00 & 100.00 & 100.00 & 100.00 \\
    Medium & \%Load & 99.00 & 99.29 & 99.29 & 99.43 & 99.57 \\
    Large & \%Load & 99.00 & 99.21 & 99.36 & 99.43 & 99.50 \\
    \bottomrule
    \end{tabular}
    }
\end{table}

@@

The medium instance $C\_104\_42\_47\_8$ has an unserved customer with a demand of 12 $m^3$ and a due time of $07:00$. Upon investigation, we find that even if we have $104$ drivers in this instance, the number of drivers starting their shift before the due time is not sufficient to serve this customer within the time window of 60 minutes that we define. So the value of $UQ$ we report in Table~\ref*{tab:all_instances} seems to be the optimal given the driver shift schedule given to our algorithm. We confirmed this observation by lifting the driver shift and overtime constraints and resolving our instances five more times. All orders are now completely served, and at each run. Table~\ref*{tab:lift_shift_constraints} compare the average values of the results of the tables \ref*{tab:all_instances} and \ref*{tab:all_instances_no_shift}. We found that for small instances, the maximum delay dropped to zero, and for medium (large) instances, it was reduced by almost 60\% (40\%) on average. This suggests that when we input a good work schedule, our algorithm works effectively to ensure that all orders are filled and that delays for first deliveries and travel costs are minimized. We can see that the average travel time decreases for all instances, except for the large one where the difference is not notable.

\begin{table}[!h]
    \centering
    \small
    \caption{Comparaison of the average results with and without shift and overtime constraints}
    \label{tab:lift_shift_constraints}
    \resizebox{0.8\textwidth}{!}{
    \begin{tabular}{lcccccccc}
    \toprule
     & \multicolumn{4}{c}{Default parameters}&\multicolumn{4}{c}{$M_T=0$, $N_T,O_T=\infty$, $H_k=0$} \\
     \cmidrule(l){2-5} \cmidrule(l){6-9}
     & $TC$ & $PUO$ & $FDD$ & $mFDD$ & $TC$ & $PUO$ & $FDD$ & $mFDD$ \\
     & (min) & ($m^3$) & (min) & (min) & (min) & ($m^3$) & (min) & (min) \\
    \midrule
    Small & 1,938.13 & 0.00 & 7.44 & 4.47 & 1,842.97 & 0.00 & 0.00 & 0.00 \\
    Medium & 15,007.28 & 10.26 & 400.45 & 46.31 & 14,879.19 & 0.00 & 74.11 & 17.87 \\
    Large & 22,045.81 & 13.26 & 935.49 & 56.93 & 22,454.09 & 0.00 & 187.51 & 34.76 \\
    \bottomrule
    \end{tabular}
    }
\end{table}
    \caption{Results with all instances without shift constraints}
    \label{tab:all_instances_no_shift}
    \begin{tabular}{llcccccccccc}
     &  & & \multicolumn{4}{c}{Avg}& \multicolumn{4}{c}{Best}\\
     \cmidrule(l){4-7} \cmidrule(l){8-12}
     &  & Demand & $TC$ & $UQ$ & $FDD$ & \multirow[c]{2}{*}{Z} & $TC$ & UQ & $FDD$ & $mFDD$ & \multirow[c]{2}{*}{Z}  \\
     &  & ($m^3$) & (min) & ($m^3$) & (min) &  & (min) & ($m^3$) & (min) & (min) & \\
    \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 1,243.5 & 0.0 & 0.0 & 1,243.5 & 1,243.5 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
     & C_13_5_8_1 & 267.0 & 745.1 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 745.1 \\
